Analyzing the Privacy Paradox Using a Nationally Representative Three-Wave Panel Study

### 2020-07-28 manuscript.RmD
- updated paper for revision

@baruhOnlinePrivacyConcerns2017 published the first empirical meta-analysis on the relations between privacy concerns and various forms of social media use (e.g., information sharing or SNS usage). 
On the basis of 37 studies, @baruhOnlinePrivacyConcerns2017 found a small and significant statistical relation between concerns about online privacy and online information sharing (_r_ = -.13, 95% CI [-.07, -.18]). 
Another more recent meta analysis by @yuMetaanalysisExplorePrivacy2020 also finds a significant bivariate relation between privacy concerns and information sharing, albeit smaller (_r_ = -.06, 95% CI [-.01, -.12]]). 
There also exist several systematic literature reviews on the privacy paradox [@barthPrivacyParadoxInvestigating2017; @gerberExplainingPrivacyParadox2018; @kokolakisPrivacyAttitudesPrivacy2017].
@kokolakisPrivacyAttitudesPrivacy2017 come to the conclusion that "the dichotomy between privacy attitude and behaviour should not be considered a paradox anymore." (p. 130)
However, the authors also note that the privacy paradox is a "complex phenomenon that has not been fully explained yet".
@barthPrivacyParadoxInvestigating2017 are more skeptical, and argue that "attempts to theoretically explain and practically solve the problem of the privacy paradox are still scarce and we feel the subject deserves far more research attention" (p. 1052).

@@

Privacy is defined as the "[...] voluntary and temporary withdrawal of a person from the general society through physical or psychological means [...]" [@westinPrivacyFreedom1967, 7]. 
Privacy captures aspects of both volitional _control_ and social _separateness_ [@braunlichLinkingLooseEnds2020; @marwickNetworkedPrivacyHow2014].
Several dimensions of privacy have been proposed.
For example, it is possible to distinguish a vertical and a horizontal level [@masurSituationalPrivacySelfdisclosure2018].
Whereas the vertical level captures privacy from authorities, institutions, or companies, horizontal privacy addresses privacy from peers, colleagues, or other people.
When it comes to concerns in general, interestingly they do not seem to be established as a stand-alone theoretical concept in psychology [@colmanDictionaryPsychology2015].
Lexically, concerns are defined as a "marked interest or regard usually arising through a personal tie or relationship" that also reflect an "uneasy state of blended interest, uncertainty, and apprehension" [@merriam-websterDefinitionConcern2018].
Concerns therefore represent both a latent _motivation_ (or increased attention), a negatively valenced _emotion_ (or affective condition), and are mostly implicit.
As a theoretical construct, privacy concerns can hence be categorized as an affective motivational disposition.
As such, there are many similarities with other concepts, including emotions (e.g., fear, anxiety), moods (e.g., dismay, fatigue), attitudes (risk perception, approval), values (e.g., autonomy, freedom), personality traits (e.g., introversion, risk avoidance), and even physiological activation (e.g., attention, arousal).
Taken together, concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened.

The online sharing of personal information, on the other hand, captures how much person-related information people share when they use the Internet, including information about their age, sex, name, address, health, and finances.
Information sharing can be differentiated from communication and self-disclosure.
Communication is broad, because it comprises all verbal and nonverbal information that is emitted [e.g., @watzlawickPragmaticsHumanCommunication2011].
Self-disclosure is narrow, because it focuses on deliberate revelations about the true self to others [e.g., @jourardTransparentSelf1964].
Information sharing is even more specific, because it addresses only person-related information but ignores other types of self-disclosure such as personal fears, values, or plans.

@@

Currently, there is a lack of studies that explicitly analyze how behavior is affected by _concerns_ in general.
Fortunately, however, we know much about the behavioral effects of related concepts such as attitudes or fears, which all can affect behavior, sometimes profoundly [@fishbeinPredictingChangingBehavior2010; @rogersCognitivePhysiologicalProcesses1983].
Emotions, perhaps the concept most closely related to concerns, have a particularly strong effect on behavior. 
By causing fight, flight, or freeze reactions, they are a primordial trigger of behavior and are considered to be an adaptive mechanism of evolved species [@dolanEmotionCognitionBehavior2002].
<!-- With their direct link to the amygdala, emotions can trigger reactions already subcortically [i.e., without activation of the more recently evolved cortical structures; @dolanEmotionCognitionBehavior2002]. -->

@@

At the same time, there are some factors that likely diminish the relation.
Most prominently, there is the so-called _attitude behavior gap_ [@fishbeinPredictingChangingBehavior2010], which states that people sometimes act against their own attitudes. 
Evidently, not everyone concerned about their physical health exercises regularly.
The explanation is simple:
Other factors such as subjective norms and perceived behavioral control also determine behavior [@ajzenIntentionsActionsTheory1985], which automatically reduces the impact of attitudes or concerns. 
Specifically, two of the most influential factors that affect online information sharing are (a) strong subjective norms [@heirmanPredictingAdolescentsDisclosure2013] and (b) expected benefits [@krasnovaOnlineSocialNetworks2010]. 
In other words, users often prioritize social support, special offers, or improved services, accepting that their privacy will be diminished.
@trepteRiskyBehaviorsHow2014 listed several factors that can additionally attenuate the relation:
lack of strength of concerns,
absence of negative personal experiences, 
or situational constraints due to social desirability.
In conclusion, also in the context of the privacy paradox it _not_ reasonable to expect a _perfect_ relation between attitudes and behaviors.
However, we should still expect to find a relation that is _small_ or _moderate_.

@@

In conclusion, in line with prior research and the within-person rationales presented above, we expect to find a small significant relation between privacy concerns and information sharing, both on the between-person level and the within-person level.

@@

@@

At the same time, the adverse effect seems plausible as well, with two potential outcomes. 
On the one hand, the long-term relation could be positive: 
If people start to share more information online, they might become increasingly aware that their privacy is at risk, thereby stirring concern [@tsay-vogelSocialMediaCultivating2018].
On the other hand, the long-term relation might also be negative:
When people share more personal information online they might become accustomed to doing so, which potentially reduces concern [for example, due to the mere exposure effect; @zajoncAttitudinalEffectsMere1968].
Finally, there could also be no long-term relation at all: 
People might have already become used to sharing information online, which stifles further cognitive or emotional processing.
This rationale is central to so-called _privacy cynicism_ [e.g., @hoffmannPrivacyCynicismNew2016].

@@

# Method
## Statistics

We follow the recommendation by @lakensJustifyYourAlpha2018 and first justify the choice of our alpha level. 
We determined adequate error margins by considering the potential implications of both false positive and false negative findings (i.e., alpha and beta errors): 
On the one hand, if we committed an alpha error, we would wrongfully conclude that people's concerns and behaviors are consistent. 
Communicating such a false result to the public might unjustly reassure people when they should be more alert.
On the other hand, if we committed a beta error, we would wrongfully conclude that individuals behave paradoxically.
Communicating such a false result would unjustly accuse people of implausible behavior, potentially causing unnecessary distress or reactance.
We consider both errors to be equally detrimental. 
Hence, we chose balanced error rates, setting a maximum error rate of 5% for both alpha and beta. 
As the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses.
Significantly smaller effects were not considered able to offer support.
The six hypotheses were tested with a one-tailed approach and the six research questions with a two-tailed approach.
On the basis of the balanced alpha-beta approach with a maximum error probability of `r alpha %>% round(3) * 100`%, a desired power of `r power %>% round(3) * 100`%, and an SESOI of $\beta$ = `r sesoi %>% my_round("beta")`, we calculated a minimum sample size of `r dollar_format(prefix = "")(round(n_apriori, 0))` respondents. 
Given the final sample size of `r dollar_format(prefix = "")(n)` respondents (see below), alpha and beta errors were balanced for our hypotheses (research questions) when we used a critical alpha of `r alpha_balanced_h  %>% round(3) * 100`% (`r alpha_balanced_rq  %>% round(3) * 100`%), resulting in a power of `r power_balanced_h %>% round(3) * 100`%  (`r power_balanced_rq %>% round(3) * 100`%) to detect small effects.

For the analyses, we used `r r_citations`.
The code, additional analyses, and a reproducible version of this manuscript can be found on the manuscript's companion website at https://xmtra.github.io/privacy-paradox/.

## Procedure and Respondents

@@

Privacy concerns were measured as a second-order factor. 
Three items captured the vertical dimension (e.g., "How concerned are you that institutions or intelligence services collect and analyze data that you disclosed on the Internet?"), and three items captured the horizontal dimension (e.g., "How concerned are you that people that you do not know might obtain information about you because of you online activities?"). 
Respondents rated all items on a 5-point scale ranging from 1 (*not at all concerned*) to 5 (*very concerned*). 
The means were _M_~t1~ = `r desc[["t1_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t2~ = `r desc[["t2_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t3~ = `r desc[["t3_pri_con_m_mean"]] %>% my_round(2)`, 
and the standard deviations _SD_~t1~ = `r desc[["t1_pri_con_m_sd"]] %>% my_round(2)`, 
_SD_~t2~ = `r desc[["t2_pri_con_m_sd"]] %>% my_round(2)`, and
_SD_~t3~ = `r desc[["t3_pri_con_m_sd"]] %>% my_round(2)`.
The two-dimensional model fit the data well, 
`r fit_txt(fit_pri_con_4)`.
The reliability was high ($\omega$~t1~ = `r reliabilityL2(fit_pri_con_4, "t1_pri_con_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t2~ = `r reliabilityL2(fit_pri_con_4, "t2_pri_con_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t3~ = `r reliabilityL2(fit_pri_con_4, "t3_pri_con_f")[["omegaL2"]] %>% my_round("std")`).
Overall, `r icc_pri_con$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.

@@

To measure respondent's level of information disclosure, they were asked how often they disclosed 10 different pieces of information on the Internet. 
The exact question was: "How often do you disclose the following pieces of information online (i.e., on the Internet)?" 
Each item was answered on a 5-point scale ranging from 1 (*never*) to 5 (*daily*). 
Factor analyses suggested a second-order factor structure with five first-order factors of two items each.
The first first-order factor subsumed financial and medical information, the second first and last name, the third place of residence and street (including house number), the fourth email address and phone number, and the fifth information about education and current job. 
The means were _M_~t1~ = `r desc[["t1_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
_M_~t2~ = `r desc[["t2_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
_M_~t3~ = `r desc[["t3_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
and the standard deviations _SD_~t1~ = `r desc[["t1_inf_sha_beh_m_sd"]] %>% my_round(2)`, 
_SD_~t2~ = `r desc[["t2_inf_sha_beh_m_sd"]] %>% my_round(2)`, and
_SD_~t3~ = `r desc[["t3_inf_sha_beh_m_sd"]] %>% my_round(2)`.
The model fit the data adequately,
`r fit_txt(fit_inf_sha_beh_4)`.
The reliability was high ($\omega$~t1~ = `r reliabilityL2(fit_inf_sha_beh_4, "t1_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t2~ = `r reliabilityL2(fit_inf_sha_beh_4, "t2_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t3~ = `r reliabilityL2(fit_inf_sha_beh_4, "t3_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`).
Overall, `r icc_inf_sha_beh$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.

@@

Respondents' attitudes toward disclosing personal information online were captured with 10 items that measured the general appraisal of disclosing the same 10 pieces of information. 
Adhering to the principle of compatibility [@fishbeinPredictingChangingBehavior2010], the items were parallel to those of the actual disclosure scale. 
Specifically, we asked: 
"Do you think that it is sensible to disclose the following pieces of information online (i.e., on the Internet)?" 
The scale ranged from 1 (*not at all sensible*) to 5 (*very sensible*). 
The means were _M_~t1~ = `r desc[["t1_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t2~ = `r desc[["t2_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t3~ = `r desc[["t3_pri_con_m_mean"]] %>% my_round(2)`, 
and the standard deviations _SD_~t1~ = `r desc[["t1_pri_con_m_sd"]] %>% my_round(2)`, 
_SD_~t2~ = `r desc[["t2_pri_con_m_sd"]] %>% my_round(2)`, and
_SD_~t3~ = `r desc[["t3_pri_con_m_sd"]] %>% my_round(2)`.
The second-order model with five first-order factors showed an adequate model fit,
`r fit_txt(fit_inf_sha_att_4)`.
The reliability was high ($\omega$~t1~ = `r reliabilityL2(fit_inf_sha_att_4, "t1_inf_sha_att_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t2~ = `r reliabilityL2(fit_inf_sha_att_4, "t2_inf_sha_att_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t3~ = `r reliabilityL2(fit_inf_sha_att_4, "t3_inf_sha_att_f")[["omegaL2"]] %>% my_round("std")`).
Overall, `r icc_inf_sha_att$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.

@@

Some of the effect sizes reported in this study are potentially not large enough to refute the privacy paradox completely. 
On the one hand, they could be a manifestation of the so-called "crud factor" [@meehlWhySummariesResearch1990, p. 204], which states that all psychosocial measures are related to one another to some extent.
On the other hand, other factors such as expected benefits might play a more important role [@dienlinExtendedPrivacyCalculus2016].
In conclusion, although our results suggest that privacy concerns and privacy attitudes are correlated with information sharing, the importance of privacy concerns should not be exaggerated.
The effects could be larger, and other variables play a role as well.

In this study we measured information sharing using self-reports. 
However, self-reports of frequent and routine behaviors are often imprecise and unreliable [@scharkowAccuracySelfreportedInternet2016]. 
This represents a profound limitation of our study. 
Whenever possible, future studies should aim to collect objective observations of behavior.

@@

Although we argue that in most circumstances privacy concerns and behavior should correlate modestly, the exact extent depends on a many boundary conditions.
Future research should hence explicitly analyze different contexts and situations. 
Building on @kokolakisPrivacyAttitudesPrivacy2017, we suggest to analyze the following boundary conditions:

@@

Specifically, we encourage analyzing privacy behaviors also from a situational perspective, accounting for temporal needs, interpersonal perceptions, contextual cues, or characteristics of communication channels [@masurSituationalPrivacySelfdisclosure2018].
For example, whereas general levels of information sharing are likely best explained by using privacy _concerns_, situational information sharing might be best explained by using privacy _heuristics_ [@sundarUnlockingPrivacyParadox2013].

>>>>

@baruhOnlinePrivacyConcerns2017 published the first empirical meta-analysis on the relations between privacy concerns and various forms of social media use (e.g., information sharing or SNS usage). 
On the basis of 37 studies, @baruhOnlinePrivacyConcerns2017 found a small and significant statistical relation between concerns about online privacy and online information sharing (_r_ = -.13, 95% CI [-.07, -.18]). 
Another more recent meta analysis by @yuMetaanalysisExplorePrivacy2020 also finds a significant bivariate relation between privacy concerns and information sharing, albeit smaller (_r_ = -.06, 95% CI [-.01, -.12]). 
There also exist several systematic literature reviews on the privacy paradox [@barthPrivacyParadoxInvestigating2017; @gerberExplainingPrivacyParadox2018; @kokolakisPrivacyAttitudesPrivacy2017].
@kokolakisPrivacyAttitudesPrivacy2017 come to the conclusion that "the dichotomy between privacy attitude and behaviour should not be considered a paradox anymore." (p. 130)
However, the authors also note that the privacy paradox is a "complex phenomenon that has not been fully explained yet".
@barthPrivacyParadoxInvestigating2017 are more skeptical, and argue that "attempts to theoretically explain and practically solve the problem of the privacy paradox are still scarce and we feel the subject deserves far more research attention" (p. 1052).

@@

Privacy is defined as the "[...] voluntary and temporary withdrawal of a person from the general society through physical or psychological means [...]" [@westinPrivacyFreedom1967, 7]. 
Privacy captures aspects of both volitional _control_ and social _separateness_ [@braunlichLinkingLooseEnds2020; @marwickNetworkedPrivacyHow2014].
People from all cultural backgrounds require privacy to fulfill fundamental needs including personal care, protected communication, intimacy, or sexuality [@altmanPrivacyRegulationCulturally1977; @westinPrivacyFreedom1967]. 
Being a universal human right [@assembly1948universal, Art. 12], privacy is essential for safety, psychosocial flourishing, and dignity.
It is driven by both individual needs and interpersonal negotiations thereof [@trepteSocialMediaPrivacy2020].

Several dimensions of privacy have been proposed.
For example, it is possible to distinguish a vertical and a horizontal level [@masurSituationalPrivacySelfdisclosure2018].
Whereas the vertical level captures privacy from authorities, institutions, or companies, horizontal privacy addresses privacy from peers, colleagues, or other people.
When it comes to concerns in general, interestingly they do not seem to be established as a stand-alone theoretical concept in psychology [@colmanDictionaryPsychology2015].
Lexically, concerns are defined as a "marked interest or regard usually arising through a personal tie or relationship" that also reflect an "uneasy state of blended interest, uncertainty, and apprehension" [@merriam-websterDefinitionConcern2018].
Concerns therefore represent both a latent _motivation_ (or increased attention), a negatively valenced _emotion_ (or affective condition), and are mostly implicit.
As a theoretical construct, privacy concerns can hence be categorized as an affective motivational disposition.
As such, there are many similarities with other concepts, including emotions (e.g., fear, anxiety), moods (e.g., dismay, fatigue), attitudes (risk perception, approval), values (e.g., autonomy, freedom), personality traits (e.g., introversion, risk avoidance), and even physiological activation (e.g., attention, arousal).
Taken together, concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened.

The online sharing of personal information, on the other hand, captures how much person-related information people share when they use the Internet.
Information sharing can be differentiated from communication and self-disclosure.
Communication is broad, because it comprises all verbal and nonverbal information that is emitted [e.g., @watzlawickPragmaticsHumanCommunication2011].
Self-disclosure is more narrow, because it focuses on deliberate revelations about the true self to others, which including aspects such as personal fears, values, or plans [e.g., @jourardTransparentSelf1964].
Information sharing is even more specific, because it addresses only person-related information,  including information about their age, sex, name, address, health, and finances.

@@

Currently, there is a lack of studies that explicitly analyze how behavior is affected by _concerns_ in general.
Fortunately, however, we know much about the behavioral effects of related concepts such as attitudes or fears, which all can affect behavior, sometimes profoundly [@fishbeinPredictingChangingBehavior2010; @rogersCognitivePhysiologicalProcesses1983].
Emotions, perhaps the concept most closely related to concerns, have a particularly strong effect on behavior. 
By causing fight, flight, or freeze reactions, they are a primordial trigger of behavior and are considered to be an adaptive mechanism of evolved species [@dolanEmotionCognitionBehavior2002].

@@

At the same time, there are some factors that likely diminish the relation.
Most prominently, there is the so-called _attitude behavior gap_ [@fishbeinPredictingChangingBehavior2010], which states that people sometimes act against their own attitudes. 
Evidently, not everyone concerned about their physical health exercises regularly.
The explanation is simple:
Other factors such as subjective norms and perceived behavioral control also determine behavior [@ajzenIntentionsActionsTheory1985], which automatically reduces the impact of attitudes or concerns.

Specifically, two of the most influential factors that affect online information sharing are (a) strong subjective norms [@heirmanPredictingAdolescentsDisclosure2013] and (b) expected benefits [@krasnovaOnlineSocialNetworks2010]. 
In other words, users often prioritize social support, special offers, or improved services, accepting that their privacy will be diminished.
Sometimes, privacy concerns do not relate information sharing, because users lack the skills, knowledge, or literacy to change their online behavior, creating feelings of apathy or cynicism [@hargittaiWhatCanReally2016; @hoffmannPrivacyCynicismNew2016].
Likewise, personal information is also often shared by others, a phenomenon described as "networked privacy" [@marwickNetworkedPrivacyHow2014], which further reduces the power of individuals to determine how much personal information can be found online.
@trepteRiskyBehaviorsHow2014 listed several factors that can additionally attenuate the relation:
lack of strength of concerns,
absence of negative personal experiences, 
or situational constraints due to social desirability.
In conclusion, also in the context of the privacy paradox it _not_ reasonable to expect a _perfect_ relation between attitudes and behaviors.
However, we should still expect to find a relation that is _small_ or _moderate_.

@@

In conclusion, in line with prior research and the within-person rationales presented above, we expect to find a small significant relation between privacy concerns and information sharing, both on the between-person level (Hypothesis 1) and the within-person level (Hypothesis 2).[^1]

@@

[^1]: To explain, with Hypothesis 1, we compare _different_ people with one another by analyzing their _average_ values across all measurements.
In other words, does a person, who is generally more concerned than others, also generally share less information than others?
With Hypothesis 2, we compare _specific_ measurements within the _same_ person.
In other words, does a person, if he/she is more concerned on T1 than on average, share more or less information on T1 than on average?

@@

At the same time, the adverse effect seems plausible as well, with two potential outcomes. 
On the one hand, the long-term relation could be positive: 
If people start to share more information online, they might become increasingly aware that their privacy is at risk, thereby stirring concern [@tsay-vogelSocialMediaCultivating2018].
On the other hand, the long-term relation might also be negative:
When people share more personal information online they might become accustomed to doing so, which potentially reduces concern [for example, due to the mere exposure effect; @zajoncAttitudinalEffectsMere1968].
Finally, there could also be no long-term relation at all: 
People might have already become used to sharing information online, which stifles further cognitive or emotional processing.
This rationale is central to _privacy cynicism_ [e.g., @hoffmannPrivacyCynicismNew2016].

@@

# Method
## Procedure and Respondents

@@

Privacy concerns were measured as a second-order factor. 
Three self-developed items captured the vertical dimension (e.g., "How concerned are you that institutions or intelligence services collect and analyze data that you disclosed on the Internet?"), and three items by @buchananDevelopmentMeasuresOnline2007 captured the horizontal dimension (e.g., "How concerned are you that people that you do not know might obtain information about you because of you online activities?"). 
Respondents rated all items on a 5-point scale ranging from 1 (*not at all concerned*) to 5 (*very concerned*). 
The means were _M_~t1~ = `r desc[["t1_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t2~ = `r desc[["t2_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t3~ = `r desc[["t3_pri_con_m_mean"]] %>% my_round(2)`, 
and the standard deviations _SD_~t1~ = `r desc[["t1_pri_con_m_sd"]] %>% my_round(2)`, 
_SD_~t2~ = `r desc[["t2_pri_con_m_sd"]] %>% my_round(2)`, and
_SD_~t3~ = `r desc[["t3_pri_con_m_sd"]] %>% my_round(2)`.
The two-dimensional model fit the data well, 
`r fit_txt(fit_pri_con_4)`.
The reliability was high ($\omega$~t1~ = `r reliabilityL2(fit_pri_con_4, "t1_pri_con_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t2~ = `r reliabilityL2(fit_pri_con_4, "t2_pri_con_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t3~ = `r reliabilityL2(fit_pri_con_4, "t3_pri_con_f")[["omegaL2"]] %>% my_round("std")`).
Overall, `r icc_pri_con$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.

@@

To measure respondent's level of information disclosure, they were asked how often they disclosed 10 different pieces of information on the Internet [@europeancommissionAttitudesDataProtection2011]. 
The exact question was: "How often do you disclose the following pieces of information online (i.e., on the Internet)?" 
Each item was answered on a 5-point scale ranging from 1 (*never*) to 5 (*daily*). 
Factor analyses suggested a second-order factor structure with five first-order factors of two items each.
The first first-order factor subsumed financial and medical information, the second first and last name, the third place of residence and street (including house number), the fourth email address and phone number, and the fifth information about education and current job. 
The means were _M_~t1~ = `r desc[["t1_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
_M_~t2~ = `r desc[["t2_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
_M_~t3~ = `r desc[["t3_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
and the standard deviations _SD_~t1~ = `r desc[["t1_inf_sha_beh_m_sd"]] %>% my_round(2)`, 
_SD_~t2~ = `r desc[["t2_inf_sha_beh_m_sd"]] %>% my_round(2)`, and
_SD_~t3~ = `r desc[["t3_inf_sha_beh_m_sd"]] %>% my_round(2)`.
The model fit the data adequately,
`r fit_txt(fit_inf_sha_beh_4)`.
The reliability was high ($\omega$~t1~ = `r reliabilityL2(fit_inf_sha_beh_4, "t1_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t2~ = `r reliabilityL2(fit_inf_sha_beh_4, "t2_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t3~ = `r reliabilityL2(fit_inf_sha_beh_4, "t3_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`).
Overall, `r icc_inf_sha_beh$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.

@@

Respondents' attitudes toward disclosing personal information online were captured with 10 items that measured the general appraisal of disclosing the same 10 pieces of information [@europeancommissionAttitudesDataProtection2011].
Adhering to the principle of compatibility [@fishbeinPredictingChangingBehavior2010], the items were parallel to those of the actual disclosure scale. 
Specifically, we asked: 
"Do you think that it is sensible to disclose the following pieces of information online (i.e., on the Internet)?" 
The scale ranged from 1 (*not at all sensible*) to 5 (*very sensible*). 
The means were _M_~t1~ = `r desc[["t1_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t2~ = `r desc[["t2_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t3~ = `r desc[["t3_pri_con_m_mean"]] %>% my_round(2)`, 
and the standard deviations _SD_~t1~ = `r desc[["t1_pri_con_m_sd"]] %>% my_round(2)`, 
_SD_~t2~ = `r desc[["t2_pri_con_m_sd"]] %>% my_round(2)`, and
_SD_~t3~ = `r desc[["t3_pri_con_m_sd"]] %>% my_round(2)`.
The second-order model with five first-order factors showed an adequate model fit,
`r fit_txt(fit_inf_sha_att_4)`.
The reliability was high ($\omega$~t1~ = `r reliabilityL2(fit_inf_sha_att_4, "t1_inf_sha_att_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t2~ = `r reliabilityL2(fit_inf_sha_att_4, "t2_inf_sha_att_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t3~ = `r reliabilityL2(fit_inf_sha_att_4, "t3_inf_sha_att_f")[["omegaL2"]] %>% my_round("std")`).
Overall, `r icc_inf_sha_att$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.

## Data Analysis

We follow the recommendation by @lakensJustifyYourAlpha2018 and first justify the choice of our alpha level. 
We determined adequate error margins by considering the potential implications of both false positive and false negative findings (i.e., alpha and beta errors): 
On the one hand, if we committed an alpha error, we would wrongfully conclude that people's concerns and behaviors are consistent. 
Communicating such a false result to the public might unjustly reassure people when they should be more alert.
On the other hand, if we committed a beta error, we would wrongfully conclude that individuals behave paradoxically.
Communicating such a false result would unjustly accuse people of implausible behavior, potentially causing unnecessary distress or reactance.
We consider both errors to be equally detrimental. 
Hence, we chose balanced error rates, setting a maximum error rate of 5% for both alpha and beta. 
As the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses.
Significantly smaller effects were not considered able to offer support.
The six hypotheses were tested with a one-tailed approach and the six research questions with a two-tailed approach.
On the basis of the balanced alpha-beta approach with a maximum error probability of `r alpha %>% round(3) * 100`%, a desired power of `r power %>% round(3) * 100`%, and an SESOI of $\beta$ = `r sesoi %>% my_round("beta")`, we calculated a minimum sample size of `r dollar_format(prefix = "")(round(n_apriori, 0))` respondents. 
Given the final sample size of `r dollar_format(prefix = "")(n)` respondents, alpha and beta errors were balanced for our hypotheses (research questions) when we used a critical alpha of `r alpha_balanced_h  %>% round(3) * 100`% (`r alpha_balanced_rq  %>% round(3) * 100`%), resulting in a power of `r power_balanced_h %>% round(3) * 100`%  (`r power_balanced_rq %>% round(3) * 100`%) to detect small effects.

For the analyses, we used `r r_citations`.
The code, additional analyses, and a reproducible version of this manuscript can be found on the manuscript's companion website at https://xmtra.github.io/privacy-paradox.

@@

The data were collected between May 2014 and May 2015---hence, after the Snowden revelations in 2013, but before the Equifax data breach in 2017, Cambridge Analytica (2018), or the implementation of the General Data Protection Regulation (2018). 
Such sweeping events, however, could affect privacy concerns, online behavior, or their mutual relation, which would limit the generalizability of our results. 
Although this is an important caveat, we have reason to believe that our findings are largely robust. 
First, additional analyses showed that the within-person relationships were stable across waves (a period of 1 year). 
Second, records of online search terms revealed that although interest in privacy-related topics and privacy-enhancing technologies increased after the Snowden revelations, it returned to prior levels after only two weeks [@preibuschPrivacyBehaviorsSnowden2015]. 
It thus seems that levels of privacy concerns and information sharing, as well as their mutual relationship, are largely robust.

In asking how much information respondents share when using the Internet in general, we automatically aggregated different platforms, contexts, and situations. However, privacy mechanisms can differ largely across contexts [@nissenbaumPrivacyContextTechnology2010] and situations [@masurSituationalPrivacySelfdisclosure2018]. Our broad perspective, therefore, is somewhat problematic and limits our capacity to understand and predict the behavior of individual people in specific situations. At the same time, aiming to maximize generalizability, we were able to extract some general underlying patterns, which can serve as a starting point for more contextualized analyses (see below).

Some of the effect sizes reported in this study are potentially not large enough to refute the privacy paradox completely. 
On the one hand, they could be a manifestation of the so-called "crud factor" [@meehlWhySummariesResearch1990, p. 204], which states that all psychosocial measures are related to one another to some extent.
On the other hand, additional factors such as expected benefits might play a more important role [@dienlinExtendedPrivacyCalculus2016].
In conclusion, although our results suggest that privacy concerns and privacy attitudes are correlated with information sharing, the importance of privacy concerns should not be exaggerated.
The effects could be larger, and other variables play a role as well.

In this study we measured information sharing using self-reports. 
However, self-reports of frequent and routine behaviors are often imprecise and unreliable [@scharkowAccuracySelfreportedInternet2016]. 
This represents a profound limitation of our study; whenever possible, future studies should aim to collect objective observations of specific types of behavior.

@@

Although we argue that in most circumstances privacy concerns and behavior should correlate modestly, the exact extent depends on a many boundary conditions.
Future research should hence explicitly analyze different contexts [@nissenbaumPrivacyContextTechnology2010] and situations [@masurSituationalPrivacySelfdisclosure2018]. 
Building on @kokolakisPrivacyAttitudesPrivacy2017, we suggest to analyze the following boundary conditions:

@@

Specifically, we encourage analyzing privacy behaviors also from a situational perspective, accounting for temporal needs, interpersonal perceptions, contextual cues, or characteristics of communication channels [@masurSituationalPrivacySelfdisclosure2018].
For example, whereas general levels of information sharing are likely best explained using privacy _concerns_, situational information sharing might be best explained using privacy _heuristics_ [@sundarUnlockingPrivacyParadox2013].
